Speed estimation for vehicles using \\SVM classification and edge detection

### 2016-06-15 Administratie/report/paper.tex
update paper

\section{Introduction}
In recent years, a lot of advanced electronics have been used to help automate driving. It is already common for some cars to have (semi-)automated parking \cite{Pohl2006} and adaptive cruise control \cite{Jurgen}. Also, a lot of safety features are being developed to increase environmental awareness of cars: pedestrian detection \cite{Gavrila2000}, automated detection of speed limit signs \cite{Torresen2004}, etc.

A feature that could be realized using the electronics that are already available in some cars, is automated maximum speed detection. This speed detection would simulate the braking distance towards the nearest obstacle and inform the user. There are various ways to achieve this. Commonly used systems in adaptive cruise control are lidar and radar.  The choice of sensor presents classic design tradeoffs \cite{Jones2001}.  Lidar  is  less  expensive  to  produce  and  easier  to package  but  performs  poorly  in  rain  and  snow. Another problem is that accumulations of mud, dust or snow on the car
can block lidar beams. Radar-based  systems,  on  the  other  hand,  can ''see'' at least 150 meters ahead in fog or rain heavy enough to cut the driver’s ability to see down to 10  meters  or  less.

Because of the problems with both this systems, we propose to use a detection system based on camera images. These images present a few advantages over a system using lidar or radar. First of all cameras are way cheaper to install. On top of that they see color (whereas lidar only sees gray scale in the infrared spectrum) and are able to gain very high resolution for more distant objects. There are several downsides to using cameras. They need light to work properly. This becomes a problem at night, because cameras can only rely on the headlights of the car. Secondly computer vision systems using camera images can use a lot op CPU power. TODO

>>>>

\section{Introduction}
The goal of this paper is to determine a maximum speed for a moving vehicle using only camera images and information from the steering column.

In recent years, a lot of advanced electronics have been used to help automate driving. It is already common for some cars to have (semi-)automated parking \cite{Pohl2006} and adaptive cruise control \cite{Jurgen}. Also, a lot of safety features are being developed to increase environmental awareness of cars: pedestrian detection \cite{Gavrila2000}, automated detection of speed limit signs \cite{Torresen2004}, etc.

A additional feature that can be realized using the electronics that are already available in some cars, is automated maximum speed detection. This speed detection would simulate the braking distance towards the nearest obstacle and inform the user. There are various ways to achieve this. Commonly used systems in adaptive cruise control are lidar and radar.  The choice of sensor presents classic design trade-offs \cite{Jones2001}.  Lidar  is  less  expensive  to  produce  and  easier  to package  but  performs  poorly  in  rain  and  snow. Another problem is that accumulations of mud, dust or snow on the car can block lidar beams. Radar-based  systems,  on  the  other  hand,  can ''see'' at least 150 meters ahead in fog or rain heavy enough to cut the driver’s ability to see down to 10  meters  or  less.

Because of the problems with both these systems, we propose to use a detection system based on camera images. These images present a few advantages over a system using lidar or radar. First of all cameras are way cheaper to install. On top of that they see color and are able to gain very high resolution for more distant objects. There are several downsides to using cameras. They require light to work properly, which becomes a problem for example at night. Secondly computer vision systems using camera images can use a lot of CPU power. Nonetheless cameras provide a cheap and accessible platform for immediate applications in real-world scenarios.

Section 2 discusses some relevant background information mostly concerning Local Binary Patterns and SVM classification. Section 3 describes the methods used in order to achieve the best results. The results are then discussed in section 4. In the last section an overview of the most important results is presented.
